---
title: "R't (art)"
author: "Matt clark"
date: "February 20, 2018"
output: html_document
---
Disclaimer: This code comes from "Phyllotaxis: Draw flowers using mathematics" a free project on DataCamp. 
https://www.datacamp.com/projects/62?utm_medium=fb%2Cig%2Can%2Cms-all&utm_source=fb_paid&utm_campaign=smartly_ppa&utm_id=5a85d82ac7e28c10880b34a9

This is a short tutorial on making "flowers" in R. Good practice in ggplot and pretty fun.

Let's set everything up

```{r }
library(ggplot2)
# This sets plot images to a nice size.
options(repr.plot.width = 4, repr.plot.height = 4)
t <- seq(0, 2*pi, length.out = 50)
x <- sin(t)
y <- cos(t)
df <- data.frame(t, x, y)
```

```{r}
# Make a scatter plot of points in a circle
p <- ggplot(df, aes(x, y))
p +geom_point()
```

```{r}
#set the arguments for a spiral
points<-500
angle<-pi*(3-sqrt(5))
t <- (1:points) * angle
x <- sin(t)
y <-cos(t)
df <- data.frame(t, x, y)
# Make a scatter plot of points in a spiral
p <- ggplot(df, aes(x*t, y*t))
p +geom_point()
```

Lets remove all this background clutter

```{r}
#Remove everything unnecessary
df <- data.frame(t, x, y)
p <- ggplot(df, aes(x*t, y*t))
p + geom_point() + theme(plot.background=element_rect(fill="white"),
panel.background = element_rect(fill = "white"),
axis.title = element_blank(), 
axis.text = element_blank(),
axis.ticks = element_blank())
```

Let's make it look a little more like a flower

```{r}
#dress it up
p + geom_point(size=8,alpha=0.5, color="darkgreen") + 
theme(plot.background=element_rect(fill="white"),
panel.background = element_rect(fill = "white"),
axis.title = element_blank(), 
axis.text = element_blank(),
axis.ticks = element_blank())
```

....This is supposed to be a dandelion...I'm not so sure though...

```{r}
#Make a dandelion
p <- ggplot(df, aes(x*t, y*t))
p +  geom_point(shape=(8),size=t,alpha=0.5, color="black") + 
theme(plot.background=element_rect(fill="white"),
panel.background = element_rect(fill = "white"),
axis.title = element_blank(), 
axis.text = element_blank(),
axis.ticks = element_blank())
```

Here's the cool one

```{r}
##final flower
angle <- 13*pi/180
points <- 2000
t <- (1:points)*angle
x <- sin(t)
y <- cos(t)
df <- data.frame(t, x, y)
p <- ggplot(df, aes(x*t, y*t))
p+ geom_point(shape=(1),size=80,alpha=0.1, color="magenta4") + 
  theme(plot.background=element_rect(fill="white"),
        panel.background = element_rect(fill = "white"),
        axis.title = element_blank(), 
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank())
```

